Attract and kill: Spinosad baited spheres to control onion maggot (\textit{Delia antiqua})

### 2019-09-11 manuscript/pest-management-science/main.tex
updated and revised based on initial feedback

\title{Spinosad baited spheres to attract and kill onion maggot (\textit{Delia antiqua})}

@@

Onion maggot (\textit{Delia antiqua}) is a pest of onions worldwide.  Current means of managing this pest rely heavily on prophylatic insecticide treatments at planting.  These options may not be viable in organic production systems or areas where resistant populations are developing.  Here we explore the efficacy of an attract and kill strategy for control of onion maggot evaluating the ability of attractive spinosad containing spheres to kill adult onion maggots and reduce field losses.  Spinosad containing spheres were able to consistently kill onion maggot adults over the course of the field season.  Pairing spinosad spheres with Delia Lure increased efficacy of the attract and kill strategy.  Performance of this strategy never achieved levels of control comparable with insecticide controls, but may be an additional tool in an integrated pest management approach where conventional pesticides are not available or additional control techniques are needed.

@@

While not as effective as insecticide controls using this attract and kill approach with spinosad spheres may be a choice where other options are not viable or as a complementary tool in an integrated pest management program.  Spinosad spheres do cause adult onion maggot mortality over extended field seasons.  This attract and kill approach could be used as an additional mortality factor in longer term management of onion maggot populations.  In situations where immediate reduction in damage from onion maggot is desired, this attract and kill approach may be desired in situations where conventional insecticide management is not available either with resistant populations or in organic production systems.

>>>>

\title{Attract and kill: Spinosad baited spheres to control onion maggot (\textit{Delia antiqua})}

@@

Onion maggot (\textit{Delia antiqua}) is a pest of onions worldwide.  Current means of managing this pest rely heavily on prophylatic insecticide treatments at planting.  These options may not be viable in organic production systems or areas where resistant populations are developing.  Here we explore the efficacy of an attract and kill strategy for control of onion maggot evaluating the ability of attractive, spinosad containing spheres to kill adult onion maggots and reduce field losses.  Spinosad containing spheres were able to consistently kill onion maggot adults over the course of the field season.  Pairing spinosad spheres with Delia Lure increased efficacy of the attract and kill strategy.  Performance of this strategy can reduce damage by onion maggot larvae compared to no insecticide controls, but did not achieved levels of control comparable with insecticide treatment. Implementation of this attract and kill strategy could be a valuable tool in situations where conventional pesticides are not available, where additional control techniques are needed, or for longer term population control of onion maggot.

@@

While not as effective as insecticide controls, using this attract and kill approach with spinosad spheres may be a choice where other options are not viable or as a complementary tool in an integrated pest management program.  Spinosad spheres do cause adult onion maggot mortality over extended field seasons.  In situations where immediate reduction in damage from onion maggot is desired, this attract and kill approach may be desired in situations where conventional insecticide management is not available either with resistant populations or in organic production systems.  Additionally, this attract and kill approach could be used as a control option where conventional pesticides are no longer effective or available. This strategy could also hold promise as an additional mortality factor in longer term management to control onion maggot populations.
